Comparative Analysis of Single--Neuron versus Dual--Neuron Output Layers in Binary Classification Neural Networks

### 2025-05-13 paper/paper.tex
docs: update author contact info and paper submission date
feat: add model parameter analysis with visualizations and comparisons
draft architecture
docs: simplify title information heading comment in LaTeX paper
docs: add binary classification task table and reference figure 3 in ViT section

%-----------------------------------------------------------------------------
% Title information – adjust author list as necessary
%-----------------------------------------------------------------------------
\title{Comparative Analysis of Single--Neuron versus Dual--Neuron Output Layers in Binary Classification Neural Networks}
\author{Khadim Hussain\\Department of Computer Science \\ University of Southern Punjab, Pakistan\\[1ex]\textit{(Additional authors may be added here)}}
\date{\today}

@@

@@

@@

\subsubsection{Vision Transformer Architecture}
Moving to a more advanced architecture, we evaluated Vision Transformer (ViT) on two different binary classification tasks. The results revealed interesting patterns in performance between the single-neuron and dual-neuron approaches.

@@

>>>>

%-----------------------------------------------------------------------------
% Title information author list
%-----------------------------------------------------------------------------
\title{Comparative Analysis of Single--Neuron versus Dual--Neuron Output Layers in Binary Classification Neural Networks}
\author{Khadim Hussain\\Department of Computer Science \\ University of Southern Punjab, Pakistan\\[1ex]\textit{(bsf2004901@ue.edu.pk)}}
\date{May 11, 2025}

@@

\textbf{Table 2: Binary classification tasks used in our experiments.}

\begin{tabular}{lll}
\hline
Task ID & Class Pair & CIFAR-10 Class IDs \\
\hline
1 & Airplane vs. Automobile & 0 vs. 1 \\
2 & Cat vs. Dog & 3 vs. 5 \\
3 & Frog vs. Ship & 6 vs. 8 \\
\hline
\end{tabular}

@@

\input{model_architectures}

@@

\subsubsection{Vision Transformer Architecture}
Moving to a more advanced architecture, we evaluated Vision Transformer (ViT) on two different binary classification tasks. The results revealed interesting patterns in performance between the single-neuron and dual-neuron approaches. Figure 3 shows a heatmap of performance differences across architectures and tasks.

@@

\input{model_parameters}
